Convective penetration probably parameterizes convective overshoot

### 2021-07-19 manuscript/ms.tex
updates with most of Daniel's recommendations

The broad category of ``convective overshoot'' in the stellar literature is an umbrella term for a few hydrodynamical processes.
The first process is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
The second process is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology.
Many studies have also examined \emph{entrainment}, the process by which convection zones expand by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
The primary focus of this work is convective penetration.

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
\caption{
Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ (see Sec.~\ref{sec:simulation_details}).
The Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line.
The top of the penetrative zone ($\delta_{0.1}$, see Sec.~\ref{sec:simulation_details}) is shown by a solid horizontal line.
(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
%Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
\label{fig:vertical_dynamics_panels}
}
\end{figure*}

Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
While a clear link between stiffness and entrainment and overshoot has seemingly emerged in these simple simulation setups, a clear mechanism for penetration remains elusive.

@@

There are hints in the literature that convective penetration may be dependent upon energy fluxes.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, and the possible importance of energy fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

@@

Convective penetration is the process by which realistic convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient towards the adiabatic.
\begin{quote}
\emph{
In this paper, we present simulations which exhibit convective penetration.
}
\end{quote}
This process is phenomenologically described in Sec.~\ref{sec:central_results}.

In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
%We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
\begin{quote}
\emph{
We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
}
\end{quote}
Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{grad_profiles.pdf}
\caption{
Measured time- and horizontally-averaged vertical profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
\label{fig:grad_profiles}
}
\end{figure}

\section{Theory}
\label{sec:theory}
We will now derive a theoretical model in which to understand convective penetration.
We will build this model through an examination of the energetics and energy fluxes within the convecting region.
In Sec.~\ref{sec:theory_equations}, we will describe our equations and problem setup and define the heat fluxes.
In Sec.~\ref{sec:theory_energy}, we will build a parameterized theory based on the kinetic energy equation and these fluxes.
We find that a description of the size of a theoretical penetration zone does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to Eqn.~\ref{eqn:temperature}.

Assuming convection reaches a time-stationary state, the heat fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\label{eqn:flux_definition}
\end{equation}
where $\Fbot$ is the flux carried at the bottom of the domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
We note that $k$ and $-\partial_z \bar{T}$ fully specify $\bar{\Frad}$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
We define the gradient and radiative gradient 
\begin{equation}
\justgrad \equiv -\partial_z \bar{T} \qquad
\gradrad \equiv \frac{\bar{\Ftot}}{k}.
\label{eqn:gradrad_definition}
\end{equation}
We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions and intuition.
Marginal stability is achieved when $\justgrad = \gradad$, a constant.
We note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{theory_profiles.pdf}
\caption{
(upper) The vertical profile of the horizontally-averaged kinetic energy fluxes $\bar{\mathcal{F}}$ realized in the simulation shown in Fig.~\ref{fig:vertical_dynamics_panels}. 
$\bar{\mathcal{F}}$ is zero at the bottom boundary, the top of the penetrative region (marked by a solid line) and again at the mid-convection zone (marked by a dashed line).
Eqn.~\ref{eqn:integral_constraint} must hold true over an integral between any two of these zeros.
Here, we have neglected the viscous portion of the fluxes; this contributes negligibly in the bulk, and is zero by construction at $z = [0, 2]$.
(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the left panel is normalized in the same manner).
\label{fig:theory_profiles}
}
\end{figure}

Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial \mathcal{K}}{\partial t}
+ \grad\dot\mathcal{F}
= \mathcal{B} - \Phi,
%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
%= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
\begin{equation}
\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
\label{eqn:kinetic_energy_1D}
\end{equation}
It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, upper panel).
We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros to find
\begin{equation}
\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
\label{eqn:integral_constraint}
\end{equation}
Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.

We now find it instructive to break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
We note that the buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
Thus, in the PZ where $\gradad > \gradrad$ (see Fig.~\ref{fig:theory_profiles}, middle panel), we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
%\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \,\,=\,\,
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
If viscous dissipation in the CZ does not balance the buoyant generation of energy in the CZ, the kinetic energy of the convective flows grows, resulting in a penetrative region.
This region grows with time until Eqn.~\ref{eqn:constraint_cz_pz_split} is satisfied.
We see that the viscous dissipation and buoyancy breaking felt by flows in the PZ determine its size.
We now parameterize the fraction of the buoyant engine consumed by CZ dissipation,
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
\label{eqn:f_defn}
\end{equation}
Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
\begin{equation}
\frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+ \frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= (1 - f).
\label{eqn:first_pz_parameterization}
\end{equation}
We will measure and report the values of $f$ achieved in our simulations in this work.
Eqn.~\ref{eqn:first_pz_parameterization} provides two limits on a hypothetical PZ:
\begin{enumerate}
\item Viscous dissipation is inefficient in the limit that $f \rightarrow 0$.
Reasonably also assuming that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the excess positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation efficiently counteracts the buoyancy work in the CZ.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
This is mathematically equivalent to standard boundary-driven convection experiments.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, bottom panel\footnote{the bulk dynamics suggest by eye $f \sim 0.5$, but due to e.g., the height dependence of $\bar{\mathcal{B}}$ in our simulations we measure $f \approx 0.74$.}).

>>>>

The broad category of ``convective overshoot'' in the stellar literature is an umbrella term for a few hydrodynamical processes \citep{zahn1991, brummell_etal_2002, korre_etal_2019}.
The first process is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
The second process is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
Many studies have also examined \emph{entrainment}, the process by which convection zones expand by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
The primary focus of this work is convective penetration.

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
\caption{
Vertical slice through a simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ (see Sec.~\ref{sec:simulation_details}).
The Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line.
The top of the penetrative zone ($\delta_{0.1}$, see Sec.~\ref{sec:simulation_details}) is shown by a solid horizontal line.
(Left) Vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly at the top of the penetration zone where $\justgrad$ departs from $\gradad$.
(Right) Temperature fluctuations, normalized by their average magnitude at each height to clearly display all dynamical features.
%Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
\label{fig:vertical_dynamics_panels}
}
\end{figure*}

Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
While a link between stiffness and entrainment and overshoot processes has seemingly emerged in previous work, a mechanism for penetration remains elusive.

@@

There are hints in the literature that convective penetration may be dependent upon energy fluxes.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this idea, and found that penetration lengths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, and the possible importance of energy fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

@@

Convective penetration is the process by which convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient to be nearly adiabatic.
\begin{quote}
\emph{
In this paper, we present simulations which exhibit convective penetration.
}
\end{quote}
This process is phenomenologically described in Sec.~\ref{sec:central_results}.

In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
%We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
\begin{quote}
\emph{
We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
}
\end{quote}
Thus, the penetration length can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the height of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{grad_profiles.pdf}
\caption{
Horizontally- and temporally-averaged profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
\label{fig:grad_profiles}
}
\end{figure}

\section{Theory}
\label{sec:theory}
In this section we derive a theoretical model of convective penetration by examining the energetics and energy fluxes in the convection and penetration zones.
In Sec.~\ref{sec:theory_equations}, we describe our equations and problem setup and define the heat fluxes.
In Sec.~\ref{sec:theory_energy}, we build a parameterized theory based on the kinetic energy (KE) equation.
We find that excess KE in the convection zone can cause a penetration zone to form.
By balancing the excess KE in the convection zone with a buoyancy-braking work term in the PZ, we are able to derive the size of the PZ.
We find that a description of the size of a theoretical penetration zone does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to Eqn.~\ref{eqn:temperature}.

Assuming convection reaches a time-stationary state, the heat fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\label{eqn:flux_definition}
\end{equation}
where $\Fbot$ is the flux carried at the bottom of the domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
The mean temperature profile $\overline{T}$ carries the radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
We note that $k$ and $-\partial_z \bar{T}$ fully specify $\bar{\Frad}$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
We define the temperature gradient and radiative temperature gradient 
\begin{equation}
\justgrad \equiv -\partial_z \bar{T} \qquad
\gradrad \equiv \frac{\bar{\Ftot}}{k}.
\label{eqn:gradrad_definition}
\end{equation}
We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions and intuition.
Marginal stability is achieved when $\justgrad = \gradad$, which we take to be a constant.
We note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{theory_profiles.pdf}
\caption{
Temporally- and horizontally-averaged profiles in an evolved simulation from the kinetic energy equation (Eqn.~\ref{eqn:kinetic_energy_1D}).
The vertical dashed line corresponds to the Schwarzschild CZ boundary, the vertical solid line corresponds to the top of the PZ.
(upper) Kinetic energy fluxes $\bar{\mathcal{F}}$, which go to zero at the bottom boundary and the top of the PZ.
(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the upper panel is similarly normalized).
The buoyancy source $\bar{\mathcal{B}}$ changes sign at the Schwarzschild boundary, and $\bar{\Phi}$ is positive-definite.
\label{fig:theory_profiles}
}
\end{figure}

Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial \mathcal{K}}{\partial t}
+ \grad\dot\mathcal{F}
= \mathcal{B} - \Phi,
%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
%= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
\begin{equation}
\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
\label{eqn:kinetic_energy_1D}
\end{equation}
Each profile in Eqn.~\ref{eqn:kinetic_energy_1D} is shown in Fig.~\ref{fig:theory_profiles} for the simulation whose dynamics are displayed in Fig.~\ref{fig:vertical_dynamics_panel}.
As in Fig.~\ref{fig:grad_profiles}, the Schwarzschild CZ boundary is plotted as a dashed line, and the top of the PZ is plotted as a solid vertical line.
In the top panel, we display $\bar{\mathcal{F}}$, neglecting the viscous terms which are only nonzero near the bottom boundary.
We see that $\bar{\mathcal{F}}$ is zero at the bottom boundary (left edge of plot) and at the top of the PZ.
In the bottom panel, we plot $\bar{\mathcal{B}}$ and $\bar{\Phi}$; we see that $\bar{\mathcal{B}}$ changes sign at the Schwarzschild CZ boundary, and that $\bar{\Phi}$ is positive-definite.

At the boundaries of the convecting region, $\bar{\mathcal{F}}$ is zero (Fig.~\ref{fig:theory_profiles}, upper panel).
We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros to find
\begin{equation}
\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
\label{eqn:integral_constraint}
\end{equation}
Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.
